---
title: "CoxPH Regression"
author: "Liyuan Hu"
date: "2021/5/27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

## Lung Cancer Dataset

We are going to apply best subset selection to the NCCTG Lung Cancer Dataset in the `survival` package. This dataset consists of survival information of patients with advanced lung cancer from the North Central Cancer Treatment Group. The proportional hazards model allows the analysis of survival data by regression modeling.
Linearity is assumed on the log scale of the hazard. The hazard ratio in Cox proportional hazard model
 is assumed constant. First, we load the data. 
 
```{r}
data(lung, package = 'survival')
head(lung)
sum(is.na(lung))
```

Then we remove the rows containing any missing data. After that, we have a total of 167 observations. 
```{r}
lung <- na.omit(lung)
lung <- lung[, -1]
dim(lung)
```
Then we change the factors into dummy variables with the `model.matrix()` function. Note that the `abess` function will automatically include the intercept.
```{r}
lung$ph.ecog <- as.factor(lung$ph.ecog)
lung <- model.matrix(~., lung)[, -1]
```
We split the dataset into a training set and a test set. The model is going to be built on the training set and later We will test the model performance on the test set.
```{r}
train <- lung[1:round((167*2)/3), ]
test <- lung[-(1:round((167*2)/3)), ]
```

## Best Subset Selection for CoxPH Regression

The `abess()` function in the `abess` package allows you to perform best subset selection in a highly efficient way. For CoxPH model, the survival information should be passed to `y` as a matrix with the first column storing the observed time and the second the status. The covariates should be passed to `x`.

```{r}
library(abess)
abess_fit <- abess(x = train[, -(1:2)], y = train[, 1:2], family = "cox")
```

<!-- By default, the `abess` function implements the ABESS algorithm with the support size changing from 0 to $\min\{p,n/log(n)p \}$ and the best support size is determined by the Generalized information Criterion (GIC). You can change the tunging criterion by specifying the argument `tune.type`. The available tuning criterion now are `gic`, `aic`, `bic`, `ebic` and `cv`. Here we give an example. -->

<!-- ```{r} -->
<!-- abess_fit.gs <- abess(x = train[, -(1:2)], y = train[, 1:2], family = "cox", tune.type = "bic") -->
<!-- ``` -->
## Interpret the Result

Hold on, we aren't finished yet. After get the estimator, we can further do more exploring work.
The output of `abess()` function contains the best model for all the candidate support size in the `support.size`. You can use some generic function to quickly draw some information of those estimators.
```{r}
# draw the estimated coefficients on all candidate support size
coef(abess_fit)

# get the deviance of the estimated model on all candidate support size
deviance(abess_fit)

# print the fitted model
print(abess_fit)
```

The `plot.abess()` function helps to visualize the change of models with the change of support size. There are 5 types of graph you can generate, including `coef` for the coefficient value, `l2norm` for the L2-norm of the coefficients, `dev` for the deviance and `tune` for the tuning value. Default if `coef`.
```{r}
plot(abess_fit, label=T)
```
The graph shows that, beginning from the most dense model, the 4th variable (`ph.ecog2`) is included in the active set until the support size reaches 0.

We can also generate a graph about the tuning value. Remember that we used the default GIC to tune the support size. 
```{r}
plot(abess_fit, type="tune")
```

The tuning value reaches the lowest point at 5. And We might choose the estimated model with support size equals 5 as our final model. 

To extract any model from the `abess` object, we can call the `extract()` function with a given `support.size`. If `support.size` is not provided, the model with the best tuning value will be returned. Here we extract the model with support size equals 6.
```{r}
best.model = extract(abess_fit, support.size = 5)
str(best.model)
```

The return is a list containing the basic information of the estimated model.

## Make a Prediction

Prediction is allowed for all the estimated model. Just call `predict.abess()` function with the `support.size` set to the size of model you are interested in. If a `support.size` is not provided, prediction will be made on the model with best tuning value. The `predict.abess()` can provide both `link`, stands for the linear predictors, and the `response`, stands for the fitted relative-risk. Here We will predict fitted relative-risk on the test data.
```{r}
fitted.results <- predict(abess_fit, newx = test, type = 'response')
```

We now calculate the C-index, i.e., the probability that, for a pair of randomly chosen comparable samples, the sample with the higher risk prediction will experience an event before the other sample or belong to a higher binary class. On this dataset, the C-index is 0.64.
```{r}
library(Hmisc)
Cindex <- max(1-rcorr.cens(fitted.results, Surv(test[, 1], test[,2]))[1],rcorr.cens(fitted.results, Surv(test[, 1], test[,2]))[1])
Cindex
```

