---
title: "Integrate SIS"
author: "Liyuan Hu"
date: "2021/5/31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

## Integrate SIS

In the case of ultra high-dimensional data, it is more effective to do feature screening first before carrying out feature selection. The `abess` package allowed users to perform the sure independent screening to pre-exclude some features according to the marginal likelihood.

## Integrate SIS in `abess` package

In the `abess()` function, to carrying out the Integrate SIS, you need to passed an integer smaller than the number of the predictors to the `screening.num`. Then the `abess()` function will first calculate the marginal likelihood of each predictor and reserve those predictors with the `screening.num` largest marginal likelihood. Then, the ABESS algorithm is conducted only on this screened subset. Here is an example.

```{r}
library(abess)
n <- 100
p <- 1000
support.size <- 3
dataset <- generate.data(n, p, support.size)
abess_fit <- abess(dataset[["x"]], dataset[["y"]], 
                   screening.num = 100)
```