---
title: "Multi-class Classification"
author: "Liyuan Hu"
date: "2021/5/31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

## Multi-class Classification

When the reponse falls into only two classes, we have logistic regression, When the number of classes is more than 2, we call it Multi-class Classification. 


## MultiClassification with abess Package

We shall conduct MultiClassification on an artifitial dataset for demonstration. The `generate.data()` function provides a simple way to generate suitable for this task. The assumpltion behind is the response vector following a multinomial distribution.
```{r}
library(abess)
n <- 100
p <- 20
support.size <- 3
dataset <- generate.data(n, p, support.size, family = "multinomial")
head(dataset$y)
dataset$beta
```
To carry out sparse mutli-task learning, you can call the `abess()` function with `family` sepecified to `mguassian`. Here is an example.

```{r}
abess_fit <- abess(dataset[["x"]], dataset[["y"]], 
                   family = "multinomial", tune.type = "cv")

coef(abess_fit, support.size = abess_fit$support.size[which.min(abess_fit$tune.value)])
```
