---
stitle: "Regularized BeSS"
author: "Liyuan Hu"
date: "2021/5/31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

## Regularized Bess

In some cases, especially under low signal-to-noise ratio (SNR) setting or predictors are highly correlated, the vallina type of $L_0$ contrained model may not be satisfying and a more sophisticated trade-off between bias and variance is needed. Under this concern, the `abess` pakcage provides option of best subset selection with $L_2$ norm regularization called the regularized bess. The model has this following form:

$$
\begin{aligned}
\min_\beta L(\beta) + \lambda \|\beta\|_2^2

\end{aligned}
$$

## Carrying out the Regularized Bess

To implement the regularized bess, you need to specify a value to the `lambda` in the `abess()` function. This `lambda` value correspondes to the penalization parameter in the model above. Here we give an example.
```{r}
library(abess)
n <- 100
p <- 20
support.size <- 3
dataset <- generate.data(n, p, support.size, snr = 1)
dataset$beta

abess_fit <- abess(dataset[["x"]], dataset[["y"]], lambda = 0.5)
coef(abess_fit, support.size = abess_fit$support.size[which.min(abess_fit$tune.value)])
```