---
title: "Positive response: Poisson and Gamma regression"
author: "Liyuan Hu, Jin Zhu, Borui Tang"
date: "2021/11/3"
output:
  html_document: 
    toc: yes
    keep_md: yes
    self_contained: no
  pdf_document:
    fig_caption: yes
    toc: yes
    toc_depth: 3
  word_document: 
    toc: yes
    keep_md: yes
vignette: |
  %\VignetteIndexEntry{Positive response: Poisson and Gamma regression} 
  %\VignetteEngine{knitr::rmarkdown} \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

## Poisson Regression

Poisson regression involves regression models in which the response variable is in the form of counts. For example, the count of number of car accidents or number of customers in line at a  reception desk. The response variable is assumed to be generated from Poisson distribution.

The Poisson regression is defined as
$$
\log(E(y_i|x_i)) = x_i^T \beta.
$$
We generate some artificial data using the following logic.
Consider a dataset containing the information of complain calls about 100 companies over a period of 10 years. `count` gives the number of complains, and the dataset also have other variables like `age`, `sex`, `job`, `education`, `region`, `marriage`. The `generate.data()` function allow you to generate simulated data. By specifying `support.size = 3`, here we set only 3 of the 5 above mentioned variable have effect on the expectation of the response `count`. 

```{r}
library(abess)
dat <- generate.data(n = 100, p = 6, support.size = 3,family = "poisson")
colnames(dat$x) <- c("age", "sex", "job", 
                     "education", "region", "marriage")
dat$beta
head(dat$x)
complain <- data.frame('count' = dat$y, dat$x)
```

## Best Subset Selection for Poisson Regression

The `abess()` function in the `abess` package allows you to perform best subset selection in a highly efficient way. You can call the `abess()` function using formula just like what you do with `lm()`. Or you can specify the design matrix `x` and the response `y`. To carry out a poisson regression, we should set the `family = "poisson"`.

```{r}
library(abess)
abess_fit <- abess(x = dat$x, y = dat$y, family = "poisson")
abess_fit <- abess(count ~ ., complain, family = "poisson")
class(abess_fit)
```


## Interpret the Result

Hold on, we aren't finished yet. After get the estimator, we can further do more exploring work.
The output of `abess()` function contains the best model for all the candidate support size in the `support.size`. You can use some generic function to quickly draw some information of those estimators.
```{r}
# draw the estimated coefficients on all candidate support size
coef(abess_fit)

# get the deviance of the estimated model on all candidate support size
deviance(abess_fit)

# print the fitted model
print(abess_fit)
```

Prediction is allowed for all the estimated models. Just call `predict.abess()` function with the `support.size` set to the size of model you are interested in. If a `support.size` is not provided, prediction will be made on the model with best tuning value.

```{r}
head(predict(abess_fit, newx = dat$x, support.size = c(3, 4)))
```


The `plot.abess()` function helps to visualize the change of models with the change of support size. There are 5 types of graph you can generate, including `coef` for the coefficient value, `l2norm` for the L2-norm of the coefficients, `dev` for the deviance and `tune` for the tuning value. Default if `coef`.

```{r}
plot(abess_fit, label = TRUE)
```
      
The graph shows that, beginning from the most dense model, the 3rd variable (job) is included in the active set until the support size reaches 0.

We can also generate a graph about the tuning value. Remember that we use the default GIC to tune the support size. 
```{r}
plot(abess_fit, type = "tune")
```

The tuning value reaches the lowest point at 3. And We might choose the estimated model with support size equals 6 as our final model. 
In fact, the tuning values of different model sizes are provided in `tune.value` of the `abess` object. You can get the best model size through the following call.

```{r}
abess_fit$support.size[which.min(abess_fit$tune.value)]
```
To extract the specified model from the `abess` object, we can call the `extract()` function with a given `support.size`. If `support.size` is not provided, the model with the best tuning value will be returned. Here we extract the model with support size equals to 3.
```{r}
best.model = extract(abess_fit, support.size = 3)
str(best.model)
best.model$beta
```

The return is a list containing the basic information of the estimated model. The best model has estimated coefficients every close to the true coefficients and it successfully recovers the correct support.

## Gamma Regression

Gamma regression can be used when you meet a positive continuous response variable such as payments for insurance claims, or the lifetime of a redundant system. It is well known that the density of Gamma distribution can be represented as a function of a mean parameter ($\mu$) and a shape parameter ($\alpha$), specifically,
$$
f(y \mid \mu, \alpha)=\frac{1}{y \Gamma(\alpha)}\left(\frac{\alpha y}{\mu}\right)^{\alpha} e^{-\alpha y / \mu} {I}_{(0, \infty)}(y),
$$
where $I(\cdot)$ denotes the indicator function. In the Gamma regression model, response variable IS assumed to follow Gamma distribution. Specifically, 
$$
y_i \sim Gamma(\mu_i, \alpha),
$$
where $1/\mu_i = x_i^T\beta$.

We apply the above procedure for gamma regression simply by changing `family = "poisson"` to `family = "gamma"`.  This time we consider the response variables as (continuous) levels of satisfaction. Also, instead of GIC, we carry out cross validation to tune the support size by setting `tune.type = "cv"` in `abess`.
```{r}
# generate data
dat <- generate.data(n = 100, p = 6, support.size = 3, family = "gamma")
colnames(dat$x) <- c("age", "sex", "job", 
                     "education", "region", "marriage")
dat$beta
head(dat$x)
complain <- data.frame('count'=dat$y, dat$x)

abess_fit <- abess(count~., complain, family = "gamma", tune.type ="cv")

# draw the estimated coefficients on all candidate support size
coef(abess_fit)
# get the deviance of the estimated model on all candidate support size
deviance(abess_fit)

# print the fitted model
print(abess_fit)

# predict results for given support sizes
head(predict(abess_fit, newx = dat$x, support.size = c(3, 4)))

plot(abess_fit, label = TRUE)

# tuning plot
plot(abess_fit, type = "tune")

# extract fitted model
best.model = extract(abess_fit, support.size = 3)
str(best.model)

# estimated coefficients
best.model$beta
```





