---
title: "Multi-Response Linear Regression"
author: "Jin Zhu, Liyuan Hu"
date: "2021/5/31"
output:
  html_document: 
    toc: yes
    keep_md: yes
    self_contained: no
  pdf_document:
    fig_caption: yes
    toc: yes
    toc_depth: 3
  word_document: 
    toc: yes
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

## Brief Introduction

Multivariate multi-response linear regression (a.k.a., multi-task learning) aims at predicting multiple responses at the same time, and thus, it is a natural extension for classical linear regression where the response is univariate. 
Multivariate multi-response linear regression (MMLR) is very helpful for the analysis of correlated response such as chemical measurements for soil samples and 
microRNAs associated with Glioblastoma multiforme cancer. 
Let $y$ is $m$-dimensional response variable, 
$x$ is $p$-dimensional predictors, 
$B \in R^{m \times p}$ is coefficient matrix, 
the MMLR model for the multivariate response is given by
$$y = B x + \varepsilon,$$
where $\varepsilon$ is $m$-dimensional random noise variable with zero mean. 

Due to the Occam's razor principal or the high-dimensionality of predictors, it is meaningful to use a small amount of predictors to conduct multi-task learning. For example, understanding the relationship between gene expression and symptoms of a disease have significant importance in identifying potential makers. Many diseases usually involve multiple manifestations and those manifestations are usually related. In some cases, it makes sense to predict those manifestations using a small but the same set of predictors. The best subset selection problem under the MMLR model is formulated as 
$$\frac{1}{2n} \| Y - XB \|_{2}^2, \text{ s.t. } \| B \|_{0, 2} \leq s,$$
where, $Y \in R^{n \times m}$ and $X \in R^{n \times p}$ record 
$n$ observations' response and predictors, respectively. 
Here $\| B \|_{0, 2} = \sum_{i = 1}^{p} I(B_{i\cdot} = {\bf 0})$, 
where $B_{i\cdot}$ is the $i$-th row of coefficient matrix $B$ and 
${\bf 0} \in R^{m}$ is an all zero vector. 

## Quick example

We use an artificial dataset to demonstrate how to solve best subset selection problem for MMLR with **abess** package. 
The `generate.data()` function provides a simple way to generate suitable for this task. 
The synthetic data have 100 observations with 3-dimensional responses and 20-dimensional predictors. Note that there are three predictors have an impact on the responses.
<!-- The assumption behind is the response vector following a multivariate gaussian distribution whose mean vector is linear to `x`. -->

```{r}
library(abess)
n <- 100
p <- 20
support.size <- 3
dataset <- generate.data(n, p, support.size, family = "mgaussian")
head(dataset$y)
dataset[["beta"]]
```

To carry out sparse multi-task learning, you can call the `abess()` function with `family` specified to `mguassian`. Here is an example.

```{r}
abess_fit <- abess(dataset[["x"]], dataset[["y"]],
                   family = "mgaussian", tune.type = "cv")
extract(abess_fit)
```

The output of `extract(abess_fit)` shows that the support set is correctly identified and the parameter estimation approach to the truth.    

Since there are three responses, we will obtain three solution path plots when calling the `plot()` function. 
The three plots corresponds to $y_1, y_2, y_3$, respectively. 
```{r}
plot(abess_fit)
```

