---
title: "Use `abess` via mlr3"
author: "Zezhi Wang"
output:
  html_document: 
    toc: yes
    keep_md: yes
    self_contained: no
  pdf_document:
    fig_caption: yes
    toc: yes
    toc_depth: 3
  word_document: 
    toc: yes
    keep_md: yes
---

This guide is to show how to use `abess` via mlr3 (Machine Learning in R universe).

First, install `mlr3` and `mlr3extralearners` (from github) if they are not in the environment.

```
devtools::install_github("mlr-org/mlr3extralearners")
install.packages("mlr3")
```

There are two learners `regr.abess` and `classif.abess`, we need to install them before use.

```{r warning=FALSE}
library(mlr3extralearners)
library(mlr3)
install_learners("regr.abess")
install_learners("classif.abess")
```

## Quick example  

We generate a design matrix $X$ containing 300 observations and each observation has 1000 predictors. The response variable $y$ is linearly related to the first, second, and fifth predictors in $X$: 
$$y = 3X_1 + 1.5X_2 + 2X_5 + \epsilon,$$
where $\varepsilon$ is a standard normal random variable.

```{r warning=FALSE}
library(abess)
synthetic_data <- generate.data(n = 300, p = 1000, 
                                beta = c(3, 1.5, 0, 0, 2, rep(0, 995)))
dat <- cbind.data.frame("y" = synthetic_data[["y"]], 
                        synthetic_data[["x"]])
```

In mlr3, learners work with the task, so we generate `task_synthetic` and split it.

```{r}
task_synthetic = as_task_regr(dat, target = "y", id = "synthetic_data")

splits = partition(task_synthetic)
```

Then we use the learner `regr.abess` to solve regression problems with abess.

```{r}
learner_regr_abess = lrn("regr.abess")
learner_regr_abess$train(task_synthetic, splits$train)
```

The method `selected_features` can show the best subset.

```{r}
learner_regr_abess$selected_features()
```

The method `predict` can use those selected features to predict on the test set.

```{r}
learner_regr_abess$predict(task_synthetic, splits$test)
```

